\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-04-20 sections/results.tex
Add: Script to generate Figure S1
Add: Section about effect of OP on variability

  In order to analyze the effect of different statistical methods on the inferred co-occurrence networks, we generated co-occurrence networks using all possible combinations of methods and estimated the variability in the networks due to each choice (Figure \ref{fig:figure2}A).
  This analysis and all subsequent analysis, unless explicitly mentioned, are performed on all the samples in the fecal microbiome transplant study.
  The networks are filtered on both association strength (0.1) and pvalue (0.05, only correlation methods) before the networks are subjected to the analyses.
  The effects of various steps on the final co-occurrence network is estimated by building a linear model of the edges of the network as a function the various step in the analysis pipeline (see Methods).
  Figure \ref{fig:figure2}A, shows the percentage of total variation among the co-occurrence networks due to the different steps of the pipeline.
  The TA step, more specifically, the choice of 16S reference database contributes the most ($\sim65.4\%$) to the variation in the networks, followed by the OP step ($\sim26.8\%$).
  This result highlights the importance of the taxonomy assignment step in the 16S data analysis workflow, implying that a change in the reference database will result in drastically different inferred networks.
  % TODO: Verify this
  The reason for this seems to derive from the mislabelling of constitutive taxa that are present in high abundance in the community, which drastically alter the nodes and hence the underlying network topology.
  In fact the variability induced by taxonomy assignment is much more significant than that due to the variability induced based on how the reference sequences themselves are identified (in the DC step).
  The residual variation (Figure \ref{fig:figure2}A) can be seen as an artifact that arises when multiple steps are changed at the same time, however this is small.

  Figure \ref{fig:figure2}B is the PCA plot of all the generated co-occurrence networks, colored by the databases in the TA step (left) and the network inference algorihtms in the NI step (right).
  In other words, each point corresponds to a network generated using different combination of tools, and captures how much the final network is affected by such choice.
  The importance of the TA step indicated in Figure \ref{fig:figure2}A is also reflected here, in the fact that most of the networks can be clearly separated based on the database used (Figure \ref{fig:figure2}B).
  However, it is also evident that some of the networks, especially those inferred using the direct association based network infernce methods, are much closer in the PCA plot regardless of the reference database used.
  % TODO: Figure out the how the OP step plays a role in the PCA plot
  % TODO: Supplementary Figure S2
  It can also be seen that the dissimilarity between the networks decreases when the low abundance \ac{otu}s are removed from the network.
  These results suggest that the most important criterion for accurate comparative analyses of co-occurrence networks is the taxonomy reference database and the level of filtering of the taxonomy tables prior to network inference.

>>>>

  In order to analyze the effect of different statistical methods on the inferred co-occurrence networks, we generated co-occurrence networks using all possible combinations of methods and estimated the variability in the networks due to each choice (Figure \ref{fig:figure2}A).
  This analysis and all subsequent analysis, unless explicitly mentioned, are performed on all the samples in the fecal microbiome transplant study.
  The networks are filtered on both association strength (0.1) and pvalue (0.05, only correlation methods) before the networks are subjected to the analyses.
  The effects of various steps on the final co-occurrence network is estimated by building a linear model of the edges of the network as a function the various step in the analysis pipeline (see Methods).
  Figure \ref{fig:figure2}A, shows the percentage of total variation among the co-occurrence networks due to the different steps of the pipeline.
  The TA step, more specifically, the choice of 16S reference database contributes the most ($\sim65.4\%$) to the variation in the networks, followed by the OP step ($\sim26.8\%$).
  This result highlights the importance of the taxonomy assignment step in the 16S data analysis workflow, implying that a change in the reference database will result in drastically different inferred networks.
  % TODO: Verify this: Figure S4
  The reason for this seems to derive from the mislabelling of constitutive taxa that are present in high abundance in the community, which drastically alter the nodes and hence the underlying network topology.
  In fact the variability induced by taxonomy assignment is much more significant than that due to the variability induced based on how the reference sequences themselves are identified (in the DC step).
  The residual variation (Figure \ref{fig:figure2}A) can be seen as an artifact that arises when multiple steps are changed at the same time, however this is small.

  Figure \ref{fig:figure2}B is the PCA plot of all the generated co-occurrence networks, colored by the databases in the TA step (left) and the network inference algorihtms in the NI step (right).
  In other words, each point corresponds to a network generated using different combination of tools, and captures how much the final network is affected by such choice.
  The importance of the TA step indicated in Figure \ref{fig:figure2}A is also reflected here, in the fact that most of the networks can be clearly separated based on the database used (Figure \ref{fig:figure2}B).
  However, it is also evident that some of the networks, especially those inferred using the direct association based network infernce methods, are much closer in the PCA plot regardless of the reference database used.
  It can also be seen that the variation (on the first two principal axes) between the networks decreases when the low abundance \ac{otu}s are removed from the network (Figure~\ref{fig:figure_s1}).
  These results suggest that the most important criterion for accurate comparative analyses of co-occurrence networks is the taxonomy reference database and the level of filtering of the taxonomy tables prior to network inference.

### 2022-04-20 sections/supplementary.tex
Change: Split up the parameter table
Add: Script to generate Figure S1
Add: Section about effect of OP on variability

@@

  \subsection*{Performance of network inference algorithms on seqtime data}

>>>>

  \subsection*{Effects of the \ac{dc} and \ac{op} steps on network variability}

    % TODO: Elaborate on this
    Figure~\ref{fig:figure_s1} describes the variation in the inferrred networks in the first two principal axes.
    This Figure is the similar to Figure~\ref{fig:figure2}B and further confirms that the variability in the networks decreases upon filtering out the taxonomic entities at low abundance.

    \begin{figure}[H]
      \centering
      \includegraphics[width=1.0\linewidth]{figure_s1.pdf}
    \end{figure}
    \begin{figure}[H]
      \centering
        \caption{
          \textbf{The variation in the inferred networks in the first two principal axes}
          The plots are colored by the tools or parameters used in the \ac{dc} step (A) and the \ac{op} step (B)
        }
      \label{fig:figure_s1}
    \end{figure}
    \FloatBarrier
    \newpage

@@

  % TODO: Write all these sections
  \subsection*{Performance of network inference algorithms on seqtime data}
  \subsection*{The JSON network format}
